---
title: 'projectmaangr Overview'
author: 'Steven J. West'
output:
  html_document:
    theme: united
    toc: yes
    toc_depth: 5
    toc_float: yes
---



# Introduction


Overview of projectmanagr R package and its use for documenting and managing projects.


---



* projectmanagr:

    + An R Package that enables Project Management using R Markdown Documents
        
    + `projectmanagr` Features include:
        
        - Filesystem layout:  
            
            - ORGANISATION -> PROGRAMMES -> PROJECTS -> PROJECT NOTES (Experiments) & PROTOCOLS (SOPs)
                
            - Projects are defined in programmes, and project notes are created to meet project deliverables
                
            - Project Notes can utilise developed Protocols (SOPs) for reproducible research output
            
        - Simple DATABASE Creation and Management 
            
            - for managing and inventory of antibodies and other important reagents
            
        - Sample Management Framework 
            
            - for managing an inventory of scientific samples 
                
            - as well as collecting data on these samples: metadata, procedure-data, experimental-data
                
        - Protocols (SOPs) Management
            
            - Insert into Experiments (Project Notes) for reproducible and documented methods and analysis
                
        - Data offset, backup and archiving
            
            - Connections to External Volumes (drives and servers) can be established for data management
                
            - Archives can be formed of Projects and data for long-term storage

```{r}
 #knitr::include_graphics("docs/images/projectmanagr-overview.svg")
```
        


* The ELN is composed of R Markdown Documents:
    
        - R Markdown allows the documentation of experiments and data analysis
        
        - R Markdown allows the embedding of R, Python, Bash and other code to form REPRODUCIBLE REPORTS for data analysis
        
        - See R4DS, R Markdown complete guide, 


```{r}
 #knitr::include_graphics("docs/images/rmd-overview.svg")
```



* The ELN is ORGANISED into PROGRAMMES:

    + COMMUNAL PROGRAMMES for Shared Resources and Data:
    
        - example: [00-NRF-SWC](00-NRF-SWC/00-NRF-SWC_index.Rmd) 
        
            - This Programme covers the Neurobiological Research Facility (Animal House)
            
            - Provides Protocols (SOPs) for the histological processing of animals
            
            - Serves as a COMMUNAL SOURCE of tissue (Brain Bank) for Histological Experiments
            
    + RESEARCHER PROGRAMMES where each scientist can manage their resources and data:
    
        - example: [01-SJW-OX](01-SJW-OX/01-SJW-OX_index.Rmd)
        
            - This Programme covers all Histological experimental work performed by Steven J. West in NDCN, Oxford 2011-2019.
            
            - Contains BMS (Biomedical Services - animal house and *in vivo* experiments) and LAB (histological and other *in vitro* experiments) Project Notes and all Project Docs and SOPs from this time.


```{r}
 #knitr::include_graphics("docs/images/projectmanagr-programmes.svg")
```



* Each PROGRAMME contains PROJECTS:

    + Projects are defined in Project Docs


```{r}
 #knitr::include_graphics("docs/images/projectmanagr-projects.svg")
```



* Each PROJECT GOALS are met with PROJECT NOTES:
    
    + Project Notes


```{r}
 #knitr::include_graphics("docs/images/projectmanagr-project-notes.svg")
```


* Each PROJECT NOTES can utilise documented PROTOCOLS (SOPs):


```{r}
 #knitr::include_graphics("docs/images/projectmanagr-sops.svg")
```



* [DPhil Thesis](01-SJW-OX/PROJECTS/SW-OX02~_DPhil_Thesis.Rmd)


---



# LAYOUT


ProjectManagr allows a flexible layout of Projects and Project Notes:


* ProjectManagr enforces the following Structure:

    + ORGANISATION - holds one or more Programmes
    
        - PROGRAMMES - holds one of more PROJECTS and Project Notes
        
            - PROJECTS/ - Contains all PROJECTS - defines GOALS and Project Notes to meet them - each project can contain Project Notes
            
                - PROJECT-NOTES - Documents actual work - they can be inside PROJECTS or in sub-DIR of PROGRAMME


* The BASIC LAYOUT IS:

    + CREATE initial ELN ORG:
    
        - This will contain all PROGRAMMES:
        
            - SHARED PROGRAMME for animal experiments -> to allow the sharing of tissues between researchers
            
            - RESEARCHER'S INDIVIDUAL PROGRAMME -> For Histology and other lab work Projects/Experiment Notes
    
    + Define PROGRAMMES:
    
        - NRF Programme to hold all TISSUES that are collected ACROSS the Lab
        
        - Each Researcher has their own Programme for their personal projects and histology/other lab experimental notes/data
        
    + Researcher defines PROJECTS
    
        - Under each PROJECT define the PROJECT NOTES that meet the PROJECT GOALS
        
    + Researcher defines PROJECT NOTES
    
        - Either under the PROJECT DOC DIR
        
        - Or in a communal DIRECTORY in the Programme Directory for experiments that are SHARED across Projects
        
            - i.e. LAB/ Directory can be used to store all LAB Experimental Notes
            
            - Placing all Expeirmental Notes into their own Directory ensures they all have the same prefix
            
            - Also avoids confusion with PREFIXES 
            
                - Difference in Prefix between PROJECTS is subtle, and can be confusing in the lab
                
                - Having a LAB/ Directory ensures each separate experiment is named: LAB~001 LAB~002 etc.
                
                
