---
title: 'projectmanagr Overview'
author: 'Steven J. West'
output:
  html_document:
    theme: united
    toc: yes
    toc_depth: 5
    toc_float: yes
---



# Overview


This document gives a new user an introduction to projectmanagr R package and its use for documenting and managing projects.


*projectmanagr : R Package for Project Management using R Markdown Documents*


```{r}
 #knitr::include_graphics("docs/images/projectmanagr-overview.svg")
```


* `projectmanagr` Features include:
    
    + Filesystem layout:
    
        - Series of Rmd documents in directory tree
        
        - ORGANISATION -> PROGRAMMES -> PROJECTS -> PROJECT NOTES (Experiments)
        
            - Supported with PROTOCOLS (SOPs REFs) & DATABASES (DB) & Samples Management Framework
            
        - Projects are defined in Programmes, and Project Notes are created to meet PROJECT DELIVERABLES
            
        - Project Notes can 
        
            - utilise developed Protocols (SOPs) for rapid documentation of work
            
            - Contain SAMPLES and data relating to them for analysis
            
            - Import RESOURCES from DATABASES for documenting their usage
        
    + SAMPLES : Sample Management Framework 
        
        - for managing an inventory of scientific samples 
            
        - as well as collecting data on these samples: metadata, procedure-data, experimental-data

    + RESOURCES : DATABASE Creation and Management 
        
        - for managing and inventory of antibodies and other important reagents

    + Protocols (SOPs & REFs) Management
    
        - REFs : References - used for general documentation of procedures used in SOPs
        
        - SOPs : Standard Operating Procedures
          
            - Define a series of procedures to achieve a specific aim : for repeated tasks for rapid documentation
        
            - Insert into Project Notes for reproducible and documented methods and analysis
            
    + Data offset, backup and archiving
        
        - Connections to External Volumes (drives and servers) can be established for data management
            
        - Archives can be formed of Projects and data for long-term storage


---



# Introduction


All work with specific goals can be modelled as projects.  The principles and insights of project management can aid in successfully meeting these goals.  


ProjectManagr wraps these project management principles and insights into an R package that allows a researcher to organise, plan, document, analyse and disseminate project work.  It uses the R Markdown format for documenting & analysing in plain text files, embedded into a filesystem structure for project management.  Rapid documentation is facilitated with user defined Protocols, that can be inserted into project work as needed.  Samples and resources are effectively managed and documented in embedded structures within R Markdown documents.  Data storage are also managed and documented in R Markdown files so large datasets can be stored, backed up, or archived on External Volumes.


This document gives a rapid introduction into using ProjectManagr, followed by suggested strategies for productive working within this system.


---



# ProjectManagr Filesystem Organisation


ProjectManagr defines a filesystem organisation for effective project management.  


* At the heart of the filesystem structure is the R Markdown Document - all documentation occurs in this format, typically in the RStudio IDE.  R Markdown Documents are used to plan, document, analyse and disseminate project work.


* R Markdown files exist at different levels in the Filesystem Structure to document work at different levels of abstraction.  Each level defines R Markdown document names & locations throughout the organisation directory tree, and syntax is defined within each R Markdown document type to link between these levels of abstraction.


---



## R Markdown Documents        


The ORGANISATION documentation is composed of R Markdown Documents in a directory tree


* R Markdown (Rmd) combines **Markdown documentation** with **code chunks** to form REPRODUCIBLE REPORTS for data analysis


* Rmd can be used for

    - plan projects & project work : Organisation Programme Project Rmds
    
    - conduct & document experiments + data collection : Project Note Rmds
    
    - perform data processing & statistical analysis : Project Note Rmds with embedded code chunks
    
    - create dissemination material from project work : Project Note Rmds & Rmd output formats


* For further details of the power of Rmd see

    - [R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/)
    
    + [R 4 Data Science](https://r4ds.had.co.nz/)

    

```{r}
 #knitr::include_graphics("docs/images/rmd-overview.svg")
```



---



## Filesystem Structure


The Filesystem Structure facilitates the documentation work at different levels of abstraction - allowing the user to move from a high level overview/summary of the Organisation, its Programmes, or the Projects defined within Programmes; down to a low-level view of project work within the Project Notes.



### Organisation






### Programmes


* The ORGANISATION is organised into PROGRAMMES:

    + COMMUNAL PROGRAMMES for Shared Resources and Data:
    
        - example: 00-NRF-SWC
        
            - This Programme covers the Neurobiological Research Facility (Animal House) at SWC
            
            - Provides communal Protocols (SOPs) for the histological processing of animal tissues
            
            - Serves as a COMMUNAL SOURCE of tissue (Tissue Bank) for Histological Experiments
            
    + RESEARCHER PROGRAMMES where each scientist can manage their resources and data:
    
        - example: 01-SJW-OSWC
        
            - This Programme covers all Histological experimental work performed by Steven J. West at SWC, UCL
            
            - Contains LAB (histological and other *in vitro* experiments) Project Notes and all Project Docs and SOPs


```{r}
 #knitr::include_graphics("docs/images/projectmanagr-programmes.svg")
```



### Projects


* Each PROGRAMME contains PROJECTS:

    + Projects are defined in Project Docs


```{r}
 #knitr::include_graphics("docs/images/projectmanagr-projects.svg")
```



### Project Notes


* Each PROJECT GOALS are met with PROJECT NOTES:
    
    + Project Notes


```{r}
 #knitr::include_graphics("docs/images/projectmanagr-project-notes.svg")
```



### Protocols


* Each PROJECT NOTES can utilise documented PROTOCOLS (SOPs):


```{r}
 #knitr::include_graphics("docs/images/projectmanagr-sops.svg")
```


See [SWC01~002~ SWC Protocols Dev](PROJECTS/SWC01/SWC01~002~_SWC_Protocols_Dev.Rmd)


TWO FORMATS:

* REFERENCES : Define **GENERIC a (SET of) procedure(s) to follow that achieve various aims**

* PROTOCOLS : Define a **single SEQUENCE of procedures to follow to achieve a desired outcome**



Use a NAMING CONVENTION

* Naming Convention : 

    + USE VERBS to define a hierarchy of protocol definitions
    
    + Define based on generic workflow: 
    
        - IMPORT (animal data) -> PERFUSE -> DISSECT -> STORE -> MEASURE -> SECTION -> MOUNT -> PROCESS -> STAIN -> CLEAR -> IMAGE





---



# PRODUCTIVE WORKING STRATEGIES




## Principles




### Only Cultivate what is Needed




## Conduct Regular Reviews of Projects


Regular reviews on all work are essential for progress:

* Help to achieve a Global Perspective

* Celebrate progress made so far - motivation

* Help to Prioritise future work


* When to perform Reviews

    + Best at START OF DAY and START OF WEEK
    
    + Monday Morning
    
    + This keeps the review fresh in your mind for remainder of the day and week
    
    + THIS IS THE MOST IMPORTANT TASK OF THE WEEK
    
        - And research shows that you are most focussed in the morning with your first work, and this focus diminishes through the day
        
        - So its best to do reviews at the start of the day and week!



### Weekly Review


* Schedule a time to look over all projects across all Programmes

    + Ascertain what the current Goals & Tasks Are
    
    + What progress has been made in past week
    
    + What should be done in the coming week



### Quarterly & Annual Review


* Schedule a time to look over all projects across all Programmes

    + What progress has been made
    
    + What are the next big Goals?  When should they be achieved by?






## Prioritise Work with TODO Lists






## Cross Referencing Work







------
---



# LAYOUT


ProjectManagr allows a flexible layout of Projects and Project Notes:


* ProjectManagr enforces the following Structure:

    + ORGANISATION - holds one or more Programmes
    
        - PROGRAMMES - holds one of more PROJECTS and Project Notes
        
            - PROJECTS/ - Contains all PROJECTS - defines GOALS and Project Notes to meet them - each project can contain Project Notes
            
                - PROJECT-NOTES - Documents actual work - they can be inside PROJECTS or in sub-DIR of PROGRAMME


* The BASIC LAYOUT IS:

    + CREATE initial ORG:
    
        - This will contain all PROGRAMMES:
        
            - SHARED PROGRAMME for shared resources -> to allow the sharing of tissues between users
            
            - USER'S INDIVIDUAL PROGRAMME -> For individual work : Projects/Experiment Notes
    
    + User defines PROJECTS
    
        - Under each PROJECT define the PROJECT NOTES that meet the PROJECT GOALS
        
    + Researcher defines PROJECT NOTES
    
        - Either under the PROJECT DOC DIR
        
        - Or in a communal DIRECTORY in the Programme Directory for experiments that are SHARED across Projects
        
            - i.e. LAB/ Directory can be used to store all LAB Experimental Notes
            
            - Placing all Expeirmental Notes into their own Directory ensures they all have the same prefix
            
            - Also avoids confusion with PREFIXES 
            
                - Difference in Prefix between PROJECTS is subtle, and can be confusing in the lab
                
                - Having a LAB/ Directory ensures each separate experiment is named: LAB~001 LAB~002 etc.
                
                
