---
title: '{{PREFIX}}~ {{TITLE}}'
author: '{{AUTHOR}}'
output:
  html_document:
    theme: united
    toc: yes
    toc_depth: 5
    toc_float: yes
---



# Objectives:



## [{{NOTE_PREFIX}}~ {{NOTE_TITLE}}]({{NOTE_LINK}})



# [{{NOTE_GOAL_TITLE}}]({{NOTE_GOAL_LINK}})



## [{{NOTE_DEL_TITLE}}]({{NOTE_DEL_LINK}})



### [{{NOTE_TASK_TITLE}}]({{NOTE_TASK_LINK}})


* overview


------



# Introduction




---



# PROTOCOL


---



## Material:





```{r, import-meta-data, message=FALSE }

# Import mouse meta data:
#mice <- read_csv("../../NRF/")
#mice %>% datatable(escape = FALSE)

```


```{r, import-material, message=FALSE, echo=FALSE, include=FALSE }

# Import mouse meta data:
#material <- read_csv("../../NRF/")

```

```{r show_material_table, echo=FALSE }

#material %>% datatable(escape = FALSE) 

```


```{r, write-material }

#material[8,]

# I am not sure how to EDIT and ADD lines to material, but need to basically take the line which says there are 22 Sections:

#  974,SC-LUM-350[16],4PFA_20_24h;30SUC_4_24h;OCT_-80_16d;16GEL_37_4h;1PBS_4,

# And convert it into two lines - one with the 6 sections taken for this exp, and one with hte remaining sections:

#  974,SC-LUM-350[6],4PFA_20_24h;30SUC_4_24h;OCT_-80_16d;16GEL_37_4h;1PBS_4_14d,LAB~001-001
#  974,SC-LUM-350[16],4PFA_20_24h;30SUC_4_24h;OCT_-80_16d;16GEL_37_4h;1PBS_4,

#  I have just manually edited the file for now!


# Some old code that may be useful in future:

#material$`SC-LUM`[11] <- "LAB~516-001 X" # 14.1I
#material$`SC-LUM`[9] <- "LAB~516-001 X" # 14.1E
#material$`SC-LUM`[10] <- "LAB~516-001 X" # 8.2G

#material$`SC-LUM`[25] <- "LAB~516-001" # 10.1E
#material$`SC-LUM`[23] <- "LAB~516-001" # 10.1D

#material$`SC-LUM`[17] <- "LAB~516-001" # 11.3C
#material$`SC-LUM`[18] <- "LAB~516-001" # 11.3D

# write_csv(material, "../../BMS/BMS~310/BMS~310~_material.csv")

```


---


### GROUPS:


Lay these out in a new TIBBLE!


01:


02:


03:
	
		
----		



## Methods:



### 1. Tissue Pre-Clearing:

		
* 1P pre-clearing: 

  	+ Dehydrate in 1-propanol ONLY - 200ul vol:

	    	- 50,75,90,95,100,100, 100%
	    	
	    	- In 15mL Falcon Tube.

	  + 100% incubation 37C 
	  
	    	- 3DAYS.

  	+ Rehydrate in PBS:

	    	- 30, 50, 75, 90, 95, 100
	    	
	    	- Sections were kept in PBS 24Hr RT.

	  + Move to PCR tubes 200ul in PBS - label
			

b. Wash:

	  a. PBSTxAz NDS 

	

### 2. 1st Ab:


|    Ab.          | conc.  |  time  |  temp  |   Vol              | groups |
| --------------- | ------ | ------ | ------ | ------------------ | ------ |
| ChAT(Gt)        | 1:100  |  4DAY  |	 37C   |  100ul per section |	02,03  |
| pCREB(RbmAb)    | 1:500  |  4DAY  |	 37C   |  100ul             |	02,03  |


Diluent: PBSTxAz NDS 

		

### 3. Wash PBSTxAz NDS:


a. 1Hr

b. 3DAY

c. 1Hr
		


### 4. 2nd Ab:


|    Ab.            | conc.  |  time  |  temp  |   Vol  | groups |
| ----------------- | ------ | ------ | ------ | ------ | ------ |
| Cy5(Rb, IgG)      | 1:400  |  4DAY  |	 37C   |  150ul |	01,02  |
| Cy3(Gt, IgG)      | 1:400  |  4DAY  |	 37C   |  150ul |	01,02  |
| YOYO1             | 1:200K |  4DAY  |  37C   |        | 01,02  |
| NeuroTrace 530    | 1:50k  |  4DAY  |  37C   |        | 01,03  |


Diluent: PBSTxAz NDS 



### 5. Wash PBSTxAz NDS:


a. 1Hr

b. O/N

c. 1Hr


	
### 6. FluoClearBABB Mounting:


a. Dehydrate in 1-propanol containing 0.3% TEA

	1. 30,50,75,90,95,100,100%


b. Move tissue to well/slide & add BABB containing 0.3% TEA

	1. Coverslip as appropriate.


c. Wait for tissue to clear prior to imaging.

		
### 7. Confocal Imaging:


* A x63wd 1um XYZ centre DRG:

* B x63wd 1um XYZ DRG:
		


---



# DATASET COLLECTION:


Visual inspection and example images to be taken:


* If any of the doulbe labelling has worked, will take datasets to practice analysis.



## A_x63wd_zStack


* Collection:

	+ Take x63wd zSlice Tile Scan of VH Motor Neurones.

	+ 1.0um XYZ voxel, 8bit depth

	+ 1.0AU 

	+ Adjust laser and gain for opt sampling.

  + Includes pCREB/pERK and ChAT channels.

  + Image taken throughout entire depth of tissue - 350um.


*This was taken to see how the labelling survived throughout the Z stack, and to see how the signal looks at 1um XYZ resolution with 1.0AU pinhole*


### B_x63wd_HiRes_zSlice


* Collection:

	+ Take x63wd zSlice Tile Scan of VH Motor Neurones.

	+ 0.31um XY voxel, 8bit depth

	+ 1.0AU 

	+ Adjust laser and gain for opt sampling.

  + Includes pCREB/pERK and ChAT channels.

  + Image taken as single Z slice towards to top of the tissue.


*This was taken to see in detail what the fluorescent labelling looked like*


---



# ANALYSIS:


---


Visual inspection and example images to be taken:


* If any of the doulbe labelling has worked, will take datasets to practice analysis.


---



## 01 Assessment of z Depth labelling


---



#### Input:


* A_x63wd_zStack



#### Output:


* 01_A_x63wd_zStack



#### Processing:


* Macro:


---



#### Re-Aligned Z Stack to XZ to explore the labelling intensity throughout Z Stack:


---



## 02 Assessment of Fluroescent Signal


---



#### Input:


* B_x63wd_HiRes_zSlice



#### Output:


* 02_B_x63wd_HiRes_zSlice



#### Processing:


* Macro:


---



#### Inspection of Fluorescence Signal at High Resolution:


---



# Discussion:













