---
title: '{{TITLE}}'
author: '{{AUTHOR}}'
{{HTML_HEADER_PROTOCOL}}
---



{{PROTOCOL_SUMMARY_HEADER}}


{{PROTOCOL_PROJECT_NOTE_LINK}}


>>>>
>>>> Provide a one sentence summary of this protocol
>>>> Each Protocol is broken into SOP and LOG sections.
>>>> This summary will be shown to users when viewing the protocol for insertion into project notes.
>>>>

This Protocol specifies the SOP for _insert_protocol_scope_


{{PROTOCOL_SUMMARY_FOOTER}}



{{PROTOCOL_GRAPHICAL_ABSTRACT_HEADER}}


>>>> SCHEMATIC representing the procedures & underlying MODEL/UNDERSTANDING of mechanisms
>>>>     - include RECOMMENDED parameter values for each step
>>>>     - include underlying MECHANISMS that happen with each step
>>>>     - This graphic and abstract serves as a QUICK REFERENCE


```{r}

knitr::include_graphics('{{PROTOCOL_GRAPHICAL_ABSTRACT_SVG}}')

```


_abstract_succinct_description_of_procedures_and_parameters_



{{PROTOCOL_GRAPHICAL_ABSTRACT_FOOTER}}



{{PROTOCOL_BACKGROUND_HEADER}}


>>>> Provide background and context to reader
>>>> Provide links to relevant project notes & data that supports the protocol procedure parameters



{{PROTOCOL_BACKGROUND_FOOTER}}



{{PROTOCOL_MATERIALS_HEADER}}


>>>> Provide a list of equipment & material
>>>> Define Equipment/Material ID - and give supplier and catalogue number
>>>> Group equipment/material together by usage/storage


>>>> SUGGEST TO add images to visualise sets of equipment/material for graphical reference


```{r equipment-material-image, fig.cap=""}

knitr::include_graphics('{{PROTOCOL_EQUIPMENT_SVG}}')

```


>>>> Consider adding notes & images on storage



{{PROTOCOL_MATERIALS_FOOTER}}



{{PROTOCOL_HEADER}}


{{PROTOCOL_SOP_HEADER}}



# _PROTOCOL_ SOP


SOP for _PROTOCOL_

>>>>
>>>> Example layout of SOP Procedures Description
>>>>   Name each Procedure SOP with short descriptive name, give brief description
>>>>     Consider adding a graphic for visual overview
>>>>   Define the standard operating procedure - series of steps & their parameters

----



## _PROCEDURE_01_


_brief_description_of_procedure_


```{r procedure-schematic, fig.cap="Procedure_schematic_caption"}

knitr::include_graphics('{{PROTOCOL_PROCEDURE_TEMPLATE_SVG}}')

```



* _PROCEDURE_

    + CONDITIONS
    
        - PARAMETERS
        
        - PARAMETERS

    + CONDITIONS
    
        - PARAMETERS
        
        - PARAMETERS


EXAMPLE:

* 1st LABEL wash

    + Buffer `PBSTxAzNDS` : PBS + 0.1% Tx + 0.1% Az + 1mg NDS
    
        - 0.4mL in 0.5mL Eppendorf

    + Conditions
    
        - RT 2min

        - 37C_Shaker 30min

        - 37C_Shaker 5min

        - RT 2min


* Notes

    + _describe_reasons_for_using_parameters_where_appropriate_



{{PROTOCOL_LOG_HEADER}}



# _PROTOCOL_ LOG


LOG of _PROTOCOL_


>>>>
>>>> Example layout of LOG Procedures Description
>>>>   Name each Procedure LOG with SAME short descriptive name as SOP procedure that data is logged from
>>>>   generate link to procedure SOP section
>>>>   define log section - what data should be logged - create template datatable for data log
>>>> 


{{PROTOCOL_LOG_SEP}}



## [] _PROCEDURE_01_ LOG


SOP : [_PROCEDURE_01_](_procedure_01_)

>>>> 
>>>> Link to SOP section that describes how to execute the steps that are logged here
>>>> 


_brief_description_of_procedure_


* LOG Notes

    + **LOG_NOTE_DESCRIPTION**:

        - _details_of_log_note__how_did_this_run_vary_from_sop_



EXAMPLE:




{{PROTOCOL_FOOTER}}



{{PROTOCOL_RESULTS_LOG_HEADER}}


Examples of expected results can be noted here.


{{PROTOCOL_RESULTS_LOG_FOOTER}}



{{PROTOCOL_TROUBLESHOOTING_HEADER}}


Troubleshooting Table: procedure, problem, potential reasons, possible solutions.



{{PROTOCOL_TROUBLESHOOTING_FOOTER}}



# CHANGE LOG


**Version 1.0 - DATE**


Created.


{{SEP02}}



