---
title: '{{TITLE}}'
author: '{{AUTHOR}}'
date: "`r Sys.Date()`"
output:
  html_document:
    theme: united
    toc: yes
    toc_depth: 5
    toc_float: yes
---



# PROJECT NOTE: 


{{PROJECT_NOTE_LINK}}


------



# PROTOCOL SUMMARY


Protocol_introduction_In_clear_and_concise_language_what_does_the_protocol_aim_to_achieve


---



# PROTOCOL BACKGROUND


links to important previous work


links to explanations of relevant theories_models


protocol_scope_what_has_this_been_tested_on


---



# EQUIPMENT & MATERIAL


* what_is_needed_to_execute_this_protocol


* include_environment_software_etc


---



# PROTOCOL


* The Protocol is a LIST of Procedures to a specific goal:

    + Each Procedure has a TITLE - briefly describes what the procedure achieves in ACTIVE TENSE
    
        - 
    
    + Each Proceudre can have a SCHEMAITC illustrating the STEPS that are to be performed
    
        - Include a caption to describe the steps illustrated
        
    + Each Procedure should then specify the STEPS:
        
        + Each step should be stated in the PASSIVE TENSE 
    
            - Methanol-triethylamine dehydration, 1st antibody incubation, etc
        
            - Tissue mounting on vibratome chuck, Microscope settings initialisation, etc
        
        + List the substeps to complete the step as sub-bullets
    
            - These should explicitly indicate what must be done - state in ACTIVE TENSE
            
                - Wash in PBS, Add MeOH-TEA, Adjust bit-depth, Glue Tissue, Section tissue, etc.
                
            - Should include photographs of the substeps being performed where possible
        
        + List the CONDITIONS in comma separate list and any repeats of the substep as sub-sub-bullets
    
            - [ ] provide a tickbox to allow a user to cross [x] when performed
        
            - Place VARIABLES where the user can paste the settings or materials or datetimes into the protocol
            
        + After all Sub-Steps and conditions, add a Notes section as sub-bullet
        
            - include the REASONS for the step/substeps
            
            - include any TIPS and ADVICE on how to execute the steps
            
    + See EXAMPLE in PROCEDURE 1
        

---



## PROCEDURE_1


procedure_1_summary_explain_purpose_of_steps



```{r procedure-schematic, fig.cap="Procedure_schematic_caption"}

knitr::include_graphics("relative/path/to/img.svg")

```



* STEP_1_PASSIVE_AB_INCUBATION

    + substep_active_wash_in_pbs
    
        - [ ] volume, temperature, time, conditions
        
        - [ ] volume, temperature, time, conditions
        
            - VARIABLES


* STEP_2_PASSIVE_AB_INCUBATION

    + substep_active_wash_in_pbs
    
        - [ ] volume, temperature, time, conditions
        
        - [ ] volume, temperature, time, conditions
        
            - VARIABLES


* STEP_3_PASSIVE_AB_INCUBATION

    + substep_active_wash_in_pbs
    
        - [ ] volume, temperature, time, conditions
        
        - [ ] volume, temperature, time, conditions
        
            - VARIABLES


* STEP_4_PASSIVE_AB_INCUBATION

    + substep_active_wash_in_pbs
    
        - [ ] volume, temperature, time, conditions
        
        - [ ] volume, temperature, time, conditions
        
            - VARIABLES
            

* Notes
    
    + REASONS
        
    + TIPS_ADVICE
    



EXAMPLE:

* Remove Ab. Diluent:
    
    + Wash: PBS
    
        - [ ] 2mL, RT, swirl by hand, ~30sec
        
            - **Add DATETIME**
        
        - [x] 2mL, RT, Shaker, 2Hr
        
        - [x] 1mL, RT, swirl by hand, ~30sec
        
    + Wash: dH2O
    
        - [x] 1mL, RT, swirl by hand, ~30sec
        
        - [x] 1mL, RT, swirl by hand, ~30sec
        
        - [x] 1mL, RT, swirl by hand, ~30sec
        

* Notes:
    
    + This will remove the NDS, Tx, Az, and the phosphate salts from the tissue


---



## PROCEDURE_2


procedure_2_summary_explain_purpose_of_steps



```{r procedure-schematic, fig.cap="Procedure_schematic_caption"}

knitr::include_graphics("relative/path/to/img.svg")

```


* STEP_1_PASSIVE_AB_INCUBATION

    + substep_active_wash_in_pbs
    
        - [ ] volume, temperature, time, conditions
        
        - [ ] volume, temperature, time, conditions
        
            - VARIABLES


* STEP_2_PASSIVE_AB_INCUBATION

    + substep_active_wash_in_pbs
    
        - [ ] volume, temperature, time, conditions
        
        - [ ] volume, temperature, time, conditions
        
            - VARIABLES


* STEP_3_PASSIVE_AB_INCUBATION

    + substep_active_wash_in_pbs
    
        - [ ] volume, temperature, time, conditions
        
        - [ ] volume, temperature, time, conditions
        
            - VARIABLES


* STEP_4_PASSIVE_AB_INCUBATION

    + substep_active_wash_in_pbs
    
        - [ ] volume, temperature, time, conditions
        
        - [ ] volume, temperature, time, conditions
        
            - VARIABLES
            

* Notes
    
    + REASONS
        
    + TIPS_ADVICE


---



## PROCEDURE_3


procedure_3_summary_explain_purpose_of_steps



```{r procedure-schematic, fig.cap="Procedure_schematic_caption"}

knitr::include_graphics("relative/path/to/img.svg")

```


* STEP_1_PASSIVE_AB_INCUBATION

    + substep_active_wash_in_pbs
    
        - [ ] volume, temperature, time, conditions
        
        - [ ] volume, temperature, time, conditions
        
            - VARIABLES


* STEP_2_PASSIVE_AB_INCUBATION

    + substep_active_wash_in_pbs
    
        - [ ] volume, temperature, time, conditions
        
        - [ ] volume, temperature, time, conditions
        
            - VARIABLES


* STEP_3_PASSIVE_AB_INCUBATION

    + substep_active_wash_in_pbs
    
        - [ ] volume, temperature, time, conditions
        
        - [ ] volume, temperature, time, conditions
        
            - VARIABLES


* STEP_4_PASSIVE_AB_INCUBATION

    + substep_active_wash_in_pbs
    
        - [ ] volume, temperature, time, conditions
        
        - [ ] volume, temperature, time, conditions
        
            - VARIABLES
            

* Notes
    
    + REASONS
        
    + TIPS_ADVICE


------



# NEXT STEPS


recommended_next_steps


link_to_other_protocols


---



# RESULTS LOG


Examples of expected results can be noted here.


---



# TROUBLESHOOTING GUIDE


Troubleshooting Guide - list: step, problem, potential reasons, possible solutions.


---



# CHANGE LOG


**Version 1.0 - DATE**


changes_made


---



# FIGURES TABLES


Example syntax for figures and tables


```{r figure-example}

#knitr::include_graphics("relative/path/to/img.svg")

```



Tables:  Can use `knitr::kable()`:

```{r table-example}

#knitr::kable(
#  mtcars[1:6, 1:6], caption = 'A subset of mtcars.'
#)

```


Can also use basic markdown syntax:



  Right     Left     Center     Default
-------     ------ ----------   -------
     12     12        12            12
    123     123       123          123
      1     1          1             1

Table:  Demonstration of simple table syntax.



-------------------------------------------------------------
 Centered   Default           Right Left
  Header    Aligned         Aligned Aligned
----------- ------- --------------- -------------------------
   First    row                12.0 Example of a row that
                                    spans multiple lines.

  Second    row                 5.0 Here's another one. Note
                                    the blank line between
                                    rows.
                                    
-------------------------------------------------------------

Table: Here's the caption. It, too, may span
multiple lines.





